Understanding Traffic Patterns and Median Speeds: Insights from Toronto’s Speed Display Program

### 2024-11-26 paper/paper.qmd
updated readme and rendered the paper

---
title: "Understanding Traffic Patterns and Median Speeds: Insights from Toronto’s Speed Display Program"
subtitle: "Northbound and Southbound Traffic Show Higher Speeds; High-Speed Vehicles Raise Median Speeds"
author: Xingjie Yao
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "This study investigates how traffic direction and high-speed vehicles affect median speeds at locations with speed display signs in Toronto. Northbound and Southbound traffic showed higher median speeds than Eastbound, and more high-speed vehicles raised the median speed. These findings highlight how road design and driver behavior influence traffic patterns. The results inform strategies to improve road safety by addressing high-speed driving and targeting high-risk areas."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
```

@@

```{r}
#| label: fig-bound
#| fig-cap: The distribution of the median speeds, measured in kilometers per hour (km/h), for vehicles traveling in each cardinal direction (Eastbound (EB), Northbound (NB), Southbound (SB), and Westbound (WB)) at monitored locations during the installation of traffic signs.
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-speeding
#| fig-cap: Illustrating the relationship between the count of vehicles observed exceeding 100 km/h and the median speed, measured in kilometers per hour (km/h), for each cardinal direction: Eastbound (EB), Northbound (NB), Southbound (SB), and Westbound (WB).
#| echo: false
#| warning: false
#| message: false

>>>>

---
title: "Understanding Traffic Patterns and Median Speeds: Insights from Toronto’s Speed Display Program"
subtitle: "Northbound and Southbound Traffic Show Higher Speeds; High-Speed Vehicles Raise Median Speeds"
author: Xingjie Yao
thanks: "Code and data are available at: [https://github.com/Stella41603/Toronto-Speeding-Analysis.git](https://github.com/Stella41603/Toronto-Speeding-Analysis.git)."
date: today
date-format: long
abstract: "This study investigates how traffic direction and high-speed vehicles affect median speeds at locations with speed display signs in Toronto. Northbound and Southbound traffic showed higher median speeds than Eastbound, and more high-speed vehicles raised the median speed. These findings highlight how road design and driver behavior influence traffic patterns. The results inform strategies to improve road safety by addressing high-speed driving and targeting high-risk areas."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(arrow)
```

@@

```{r}
#| label: fig-bound
#| echo: false
#| warning: false
#| message: false
#| fig-cap: The distribution of the median speeds, measured in kilometers per hour (km/h), for vehicles traveling in each cardinal direction Eastbound (EB), Northbound (NB), Southbound (SB), and Westbound (WB), at monitored locations during the installation of traffic signs.

@@

```{r}
#| label: fig-speeding
#| fig-cap: Illustrating the relationship between the count of vehicles observed exceeding 100 km/h and the median speed, measured in kilometers per hour, for each cardinal direction, Eastbound (EB), Northbound (NB), Southbound (SB), and Westbound (WB).
#| echo: false
#| warning: false
#| message: false
